Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-08 main.tex

Let $\Delta$ be the countable (unranked) alphabet obtained
from $\Omega$ by:
$\Delta = \Deltai \uplus \Deltac \uplus \Deltar$, with
$\Deltai = \Delta_0$,
$\Deltac = \{ \; \call{a} \mid a \in \Omega_{>0} \}$,
$\Deltar = \{ \; \return{a} \mid a \in \Omega_{>0} \}$.

\noindent
We associate to $\Delta$
a label theory $\hat{\Phi}$
like in Section~\ref{sec:SWVPA-def},
%
\noindent
and we define a linearization of trees of $\T_\Omega$ into
words of $\Delta^*$ as follows:
\begin{description}
\item $\lin(a) = a$ for all $a \in \Omega_0$,
\item $\lin\bigl( b(t_1, \ldots, t_k)\bigr) =
       \call{b} \; \lin(t_1) \ldots \lin(t_k) \; \return{b}$
       when $b \in \Omega_k$ for $1 \leq k \leq M$.
\end{description}

\begin{proposition}\label{lem:SWTA}
For all \SWTA $A$ over~$\Omega$, $\Semiring$ commutative, and $\bar\Phi$,
there exists an effectively constructible \SWVPA $A'$ over
$\Delta$, $\Semiring$ and $\hat\Phi$
such that for all $t \in \T_\Omega$, $A'\bigl(\lin(t)\bigr) = A(t)$.
\end{proposition}
%
\begin{proof}
Let $A = \< Q, \init, \bar{\wei} >$ where $\bar{\wei}$ is presented as above by a function
    %
We build
$A' = \< Q', P', \init', \bar{\wei}', \final' >$,
%computing over $\Delta = \Omegai \uplus \Omegac \uplus \Omegar$,
where $Q' = \bigcup_{k=0}^{M} Q^k$ is the set of sequences of state symbols of $A$,
of length at most $M$, including the empty sequence denoted by~$\varepsilon$,
and where $P' = Q'$ and $\bar\wei$ is defined by:

>>>>

Let $\hat\Omega$ be the countable (unranked) alphabet obtained
from $\Omega$ by:
$\hat\Omega = \Deltai \uplus \Deltac \uplus \Deltar$, with
$\Deltai = \Omega_0$,
$\Deltac = \{ \; \call{a} \mid a \in \Omega_{>0} \}$,
$\Deltar = \{ \; \return{a} \mid a \in \Omega_{>0} \}$.

\noindent
We associate to $\hat\Omega$
a label theory $\hat{\Phi}$
like in Section~\ref{sec:SWVPA-def},
%
\noindent
and we define a linearization of trees of $\T_\Omega$ into
words of ${\hat\Omega}^*$ as follows:
\begin{description}
\item $\lin(a) = a$ for all $a \in \Omega_0$,
\item $\lin\bigl( b(t_1, \ldots, t_k)\bigr) =
       \call{b} \; \lin(t_1) \ldots \lin(t_k) \; \return{b}$
       when $b \in \Omega_k$ for $1 \leq k \leq M$.
\end{description}

\begin{proposition}\label{lem:SWTA}
For all \SWTA $A$ over~$\Omega$, $\Semiring$ commutative, and $\bar\Phi$,
there exists an effectively constructible \SWVPA $A'$ over
$\hat\Omega$, $\Semiring$ and $\hat\Phi$
such that for all $t \in \T_\Omega$, $A'\bigl(\lin(t)\bigr) = A(t)$.
\end{proposition}
%
\begin{proof}
Let $A = \< Q, \init, \bar{\wei} >$ where $\bar{\wei}$ is presented as above by a function
    %
We build
$A' = \< Q', P', \init', \bar{\wei}', \final' >$,
%computing over $\Delta = \Omegai \uplus \Omegac \uplus \Omegar$,
where $Q' = \bigcup_{k=0}^{M} Q^k$ is the set of sequences of state symbols of $A$,
of length at most $M$, including the empty sequence denoted by~$\varepsilon$,
and where $P' = Q'$ and $\bar\wei$ is defined by:
